Maximum Entropy Spectral Analysis: a case study

### 2021-03-26 paper/mesa.tex
Tiny change in paper
Added PE to conclusions

The maximisation of entropy, supplemented by evidence in the form of constraints to which the sought-for probability distribution must obey,
gives rise to several of the most common probability distributions utilised commonly by data scientists. For instance, whenever the only constraint available is the normalisation of the probability distribution, the entropy is maximised by the uniform distribution. 
If the information available is instead the expected value -- the mean -- entropy is maximised by the  exponential distribution.

@@

}.
Toeplitz matrices are asymptotically equivalent to circulant matrices and thus diagonalised by the discrete Fourier transform base\cite{Gray}.
%R. M. Gray, Foundations and Trends⃝R in Communications and Information Theory 2, 155 (2005), URL https://doi.org/10.1561/0100000006.
Some simple algebra shows that the time-domain multivariate Gaussian can be transformed into the equivalent frequency domain 
probability distribution:
\begin{align}
p&\left((\tilde{x}_1, \ldots, \tilde{x}_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det S\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i}\tilde{x}_i^2S^{-1}_{i} \right)\,,
\end{align}
where the matrix $S = S_i \delta_{ij}$ is an $n\times n$ diagonal matrix whose elements are the PSD $S(f)$ calculated at frequency $f_i$.
Many readers will recognise the familiar form of the Whittle likelihood that stands at the basis of the \emph{matched filter} method\cite{prob_information_theory}
%P. M. Woodward, D. W. Fry, and W. Higinbotham, Probability and information theory, with applications to radar; 2nd ed. (Pergamon Press, Oxford, 1964), URL http://cds.cern.ch/record/2031792.
and of gravitational waves data analysis, e.g. \cite{Finn_1992, FINDCHIRP}.
Thanks to MAXENT, the problem of defining the probability distribution describing a wide-sense stationary process is thus 
entirely reduced to the estimation of the PSD or, equivalently, the auto-covariance function.

@@

First of all, as short time series are required to produce meaningful PSD estimations, it can be suitable in the context of PE...
\textbf{##############PE part here#############}

>>>>

@@

}.
Toeplitz matrices are asymptotically equivalent to circulant matrices and thus diagonalised by the discrete Fourier transform base\cite{Gray}.
%R. M. Gray, Foundations and Trends⃝R in Communications and Information Theory 2, 155 (2005), URL https://doi.org/10.1561/0100000006.
Some simple algebra shows that the time-domain multivariate Gaussian can be transformed into the equivalent frequency domain 
probability distribution:
\begin{align}\label{eq:Whittle}
p&\left((\tilde{x}_1, \ldots, \tilde{x}_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det S\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i}\tilde{x}_i^2S^{-1}_{i} \right)\,,
\end{align}
where the matrix $S = S_i \delta_{ij}$ is an $n\times n$ diagonal matrix whose elements are the PSD $S(f)$ calculated at frequency $f_i$.
Many readers will recognise the familiar form of the Whittle likelihood that stands at the basis of the \emph{matched filter} method\cite{prob_information_theory}
%P. M. Woodward, D. W. Fry, and W. Higinbotham, Probability and information theory, with applications to radar; 2nd ed. (Pergamon Press, Oxford, 1964), URL http://cds.cern.ch/record/2031792.
and of gravitational waves data analysis, e.g. \cite{Finn_1992, FINDCHIRP}.
Thanks to MAXENT, the problem of defining the probability distribution describing a wide-sense stationary process is thus 
entirely reduced to the estimation of the PSD or, equivalently, the auto-covariance function.

@@

First of all, as short time series are required to produce meaningful PSD estimations, it can be suitable in the context of parameter estimation. To compute the posterior distribution for the parameters the knowledge of prior distributions and Likelihood for noise is required. A full description for noise can be obtained in Fourier Domain by the choice of the Whittle Likelihood \ref{eq:Whittle}, that is completely determined by the knowledge of the PSD for noise. While traditional methods might be instable with respect to the hypothesis (such as Welch) or require a Large number of prior assumptions, MESA represents a stable and parsimonious way to characterize noise and compute posterior distributions.
